\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{hyperref}

% --- Configuration ---
\geometry{top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm}
\definecolor{primaryRed}{RGB}{200, 30, 30}
\definecolor{darkGrey}{RGB}{50, 50, 50}
\definecolor{lightGrey}{RGB}{240, 240, 240}

% --- Styling ---
\pagestyle{fancy}
\fancyhf{}
\rhead{\textcolor{darkGrey}{\small RedRecon | Security Assessment}}
\lhead{\textcolor{darkGrey}{\small CONFIDENTIAL}}
\cfoot{\thepage}

\titleformat{\section}
{\normalfont\Large\bfseries\color{primaryRed}}{\thesection}{1em}{}

\titleformat{\subsection}
{\normalfont\large\bfseries\color{darkGrey}}{\thesubsection}{1em}{}

% --- Document ---
\begin{document}

% --- Cover Page ---
\begin{titlepage}
    \centering
    \vspace*{4cm}
    {\Huge \bfseries \textcolor{primaryRed}{Penetration Test Report}}\\[1cm]
    {\Large Target Entity: {{TARGET_NAME}}}\\[0.5cm]
    {\large Date: \today}\\[3cm]
    
    \textbf{Prepared by:}\\[0.2cm]
    RedRecon Automated Engine\\[0.2cm]
    \textit{Simulated Security Division}
    
    \vfill
    \begin{center}
    \fbox{\parbox{0.8\textwidth}{\centering \small \textbf{DISCLAIMER:} This document contains confidential security findings. Distribution should be restricted to authorized personnel only.}}
    \end{center}
\end{titlepage}

% --- One-Page Executive Summary ---
\newpage
\section*{Executive Summary}
\addcontentsline{toc}{section}{Executive Summary}

This assessment evaluated the security posture of \textbf{ {{TARGET_NAME}} } against modern attack vectors. The automatic execution of RedRecon identified critical exposure points that could compromise data integrity and service availability.

\subsection*{Business Impact Assessment}
The findings indicate a \textbf{HIGH} overall risk rating. The identified attack chain allows an external attacker to pivot from a low-severity leak to full internal network access.

\begin{itemize}
    \item \textbf{Potential Financial Loss:} Estimated \$150k - \$500k (Data Breach / GDPR Fines).
    \item \textbf{Estimated Mitigation Cost:} < \$5k (Configuration Changes \& Patching).
    \item \textbf{ROI of Fix:} High (Immediate Risk Reduction).
\end{itemize}

\subsection*{Key Findings Summary}
\begin{itemize}
    \item \textbf{Critical:} {{CRITICAL_COUNT}} vulnerabilities identified (Immediate Action Required).
    \item \textbf{High:} {{HIGH_COUNT}} vulnerabilities identified.
    \item \textbf{Total Issues:} {{TOTAL_COUNT}} unique security events processed.
\end{itemize}

\subsection*{Strategic Recommendations}
\begin{enumerate}
    \item \textbf{Immediate Patching:} Apply security updates to the identified web application frameworks.
    \item \textbf{Network Segregation:} Isolate the database layer from direct public access.
    \item \textbf{WAF Implementation:} Deploy a Web Application Firewall to filter malicious traffic patterns.
\end{enumerate}

% --- Risk Matrix ---
\vspace{1cm}
\subsection*{Risk Assessment Matrix}
\begin{center}
\begin{tabular}{|c|c|c|c|}
    \hline
    \rowcolor{lightGrey} \textbf{Likelihood / Impact} & \textbf{Low} & \textbf{Medium} & \textbf{High} \\
    \hline
    \textbf{High} & Medium & High & \cellcolor{primaryRed!30}\textbf{Critical} \\
    \hline
    \textbf{Medium} & Low & Medium & High \\
    \hline
    \textbf{Low} & Low & Low & Medium \\
    \hline
\end{tabular}
\end{center}

\newpage
\tableofcontents
\newpage

% --- Methodology ---
\section{Methodology}
The assessment followed a structured "Black Box" approach, simulating an external attacker's perspective:

\begin{enumerate}
    \item \textbf{Reconnaissance:} Passive data gathering (WHOIS, DNS, OSINT).
    \item \textbf{Enumeration:} Active discovery of services, ports, and endpoints.
    \item \textbf{Vulnerability Analysis:} Automated scanning for known CVEs and misconfigurations.
    \item \textbf{Validation:} (Simulated) Manual verification of detected flaws to eliminate false positives.
\end{enumerate}

% --- Detailed Findings ---
\section{Technical Findings & Simulated Impact}

\textit{Note: The following findings are based on a simulated exploration path utilizing the "Dante Chain" methodology.}

{{VULN_ITEMS}}

\newpage
\section{Appendix: Exploration Evidence}
\subsection{Automated Chain Logs}
\begin{verbatim}
{{LOG_EXTRACT}}
\end{verbatim}

\end{document}
