\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=2.5cm]{geometry}

% Meta
\title{\textbf{RedRecon Assessment Report}}
\author{Automated Pentest Engine v2.0}
\date{\today}

\begin{document}

\maketitle
\thispagestyle{empty}

\begin{abstract}
This document contains the automated security assessment results for \textbf{target-corp.com}. 
The scan was performed using RedRecon with dynamic proxy rotation to ensure accurate and evasion-resistant enumeration.
\end{abstract}

\tableofcontents
\newpage

\section{Executive Summary}
RedRecon identified a total of \textbf{21} potential issues. 
The assessment focused on external attack surface management and automated vulnerability discovery.

\begin{itemize}
    \item \textbf{Target:} target-corp.com
    \item \textbf{Scan Duration:} 0.087s
    \item \textbf{Proxies Rotated:} 12
\end{itemize}

\section{Vulnerability Findings}

\subsection{High Severity}
\noindent
\textbf{Issue:} SQL Injection (Blind) \\
\textbf{Impact:} Allows unauthorized access to database contents. \\
\textbf{Remediation:} Use parameterized queries/prepared statements.

\subsection{Medium Severity}
\noindent
\textbf{Issue:} Reflected Cross-Site Scripting (XSS) \\
\textbf{Impact:} Execution of malicious scripts in user browser. \\
\textbf{Remediation:} Context-aware output encoding.

\section{Detailed Logs}
\begin{verbatim}
[INF] Starting RedRecon...
[+] Found IP: 104.28.2.14
[+] VULN: SQLi at /login.php
[+] VULN: XSS at /search?q=
[INF] Scan Finished.
\end{verbatim}

\newpage
\section{Disclaimer}
This report was generated automatically. All findings should be verified manually before taking remediation actions. 
The data contained herein is strictly confidential.

\end{document}
